Continuations via Negative Information Flow

### 2012-02-14 dual.tex
more constructions
_

@@

@@

\item {{(-b1) * b2}} is not the same as {{b1 * (-b2)}} as there is no
  isomorphism to translate from one to the other.

@@

\item {{-(-b)}} is not the same as {{b}} as there is no isomorphism
  that goes from one to the other.

@@

>>>>

%subcode{proof} include main
%@ c : b2 + b1 <-> b2 + b3
%@@ trace c : b1 <-> b3

@@

Double Negation

{{b <-> -(-b)}}

\begin{center}
  \includegraphics{diagrams/double_neg.pdf}
\end{center}

Negation distributes over {{+}}.

{{-(b1 + b2) <-> (b1) + (-b2)}}

\begin{center}
  \includegraphics{diagrams/dist_neg_plus.pdf}
\end{center}

Lifting negation out of {{*}}.

{{(-b1) * b2 <-> -(b1 * b2) <-> b1 * (-b2)}}

\begin{center}
  \includegraphics{diagrams/mult_neg.pdf}
\end{center}

@@

@@

@@

\item Which operations can be lifted to work on negative types?

\item Can the operational semantics for {{langRevEE}} be an
  interpreter that is implemented in {{langRevT}} (similar to how the
  the tree traversal interpreter was implemented). This would imply
  the existence of a more powerful construction than Int, wherein the
  products would also be preserved. This is possibly worth a paper in
  itself.
